Using a Deep Autoencoder Model to Characterize Air Pollution

### 2021-08-04 paper-draft/paper.tex
Removed unncecessary files from paper-draft/

\documentclass{article}
\usepackage[backend=biber, style=authoryear-icomp]{biblatex}
\usepackage{blindtext}
\usepackage{multicol}
\usepackage[document]{ragged2e}
\usepackage[pass, letterpaper]{geometry}
%\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{subcaption}
\addbibresource{ref.bib}

@@

\section{Results}
First, we wanted to explore the correlation between days in our dataset. We calculated
the correlation coefficients and created a correlation matrix of the days that had
correlation coefficients of the highest magnitude.\par

% pipeline
\begin{figure}[h]
\includegraphics[width=\textwidth]{/home/nicks/Documents/paper-draft/images/corr_matrix_25.png}
\caption{Correlation Matrix}
\label{fig:pipeline}
\end{figure}

We compared the percent explained variance across one hundred twenty dimensions for
the encoded values generated by the PCA and autoencoder models as well as for the unencoded
values by using a simple linear regression. While PCA was overall less noisy, we found that
the autoencoder model achieved a much higher explainable variance for the first few dimensions.
\\ \note{Note that results graphs are placeholders}
% ae vs pca linegraph
\begin{figure}[h!]

@@

By selecting from a list the top two hundred highly-populated cities, we found that nearly
all of them were located near the center of the clustering. Conversely, we found that many 
of the outliers were smaller cities in rural locations.

\section{Discussion}

>>>>

\documentclass{article}
\usepackage[backend=biber, style=authoryear-icomp]{biblatex}
\usepackage{blindtext}
\usepackage{multicol}
\usepackage[document]{ragged2e}
\usepackage[pass, letterpaper]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{subcaption}
\addbibresource{ref.bib}

@@

\section{Results}
We compared the percent explained variance across one hundred twenty dimensions for
the encoded values generated by the PCA and autoencoder models as well as for the unencoded
values by using a simple linear regression. While PCA was overall less noisy, we found that
the autoencoder model achieved a much higher explainable variance for the first few dimensions.
\\ \note{Note that results graphs are placeholders}
% ae vs pca linegraph
\begin{figure}[h!]

@@

By selecting from a list the top two hundred highly-populated cities, we found that nearly
all of them were located near the center of the clustering. Conversely, we found that many 
of the outliers were smaller cities in rural locations. \par

To further explore the meaning of the hidden dimensions, we calculated the Pearson correlation
coefficient of the normalized timeseries data and the embeddings. The Pearson correlation
coefficient allows us allows us to observe the strength of the linear correlation between
the encoded and unencoded values. 
\begin{equation*}
    r_{XY}=\frac{cov(X,Y)}{\sigma_{X} \cdot \sigma_{Y}}
\end{equation*}
\textit{Where cov(X,Y) is the covariance between X and Y \\
and $\sigma_{X},\sigma{Y}$ are the standard deviations of X and Y respectively}

\vspace{0.1in}

We calculated the correlation coefficients and created a correlation matrix of the days that had
correlation coefficients of the highest magnitude.\par

% pipeline
\begin{figure}[h]
\includegraphics[width=\textwidth]{/home/nicks/Documents/paper-draft/images/corr_matrix_25.png}
\caption{Correlation Matrix}
\label{fig:matrix}
\end{figure}
\section{Discussion}
